### 2014-03-15 src/discussion.Rnw
Add x\% selection for operators

Considering mutation operators, only three operators \textit{NC,RC,DC} had
consistent results (and only for original test suites). On considering
operator selection, n-selection strategy had high accuracy and consistency
(though low reduction ratio) until 7-selection (removing seven most numerous
operators) for both generated and original test suites. Javalanche did not
have a high mutation reduction ratio, though it had high accuracy for both
kinds of test suites. The other operator selection methods performed poorly
on generated test suites, while they had high accuracy and reasonable
stability on original test suites. However, for comparable mutation
reduction, they performed worse than random sampling strategies.

>>>>

While the x\% per operator strategy produced consistent results, its
consistency was lower than \textit{sample(x)} results, and was either on
par or below \textit{sample(x)} for accuracy.

Considering mutation operators, only three operators \textit{NC,RC},and
\textit{DC} had consistent results (and only for original test suites).
On considering operator selection, n-selection strategy had high accuracy
and consistency (though low reduction ratio) until 7-selection (removing
seven most numerous operators) for both generated and original test suites.
Javalanche did not have a high mutation reduction ratio, though it had high
accuracy for both kinds of test suites. The other operator selection methods
performed poorly on generated test suites, while they had high accuracy
and reasonable stability on original test suites. However, for comparable
mutation reduction, they performed worse than random sampling strategies.
